\large Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2019-01-09 Dissertation/Defense/scitech19_presentation.tex
added mars presentation

\setbeamertemplate{footline}%{split theme}
{%
  \leavevmode%
  \hbox{\begin{beamercolorbox}[wd=.7\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm plus1fill]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.5\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm]{title in head/foot}
    \usebeamerfont{title in head/foot}\mypaper\hfill \insertframenumber/\inserttotalframenumber
    \usebeamerfont{title in head/foot}\hfill \insertframenumber/\inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
} \setbeamercolor{box}{fg=black,bg=yellow}

\title[Multi-Robot Probabilistic Mapping and Exploration]{\large Multi-Robot Probabilistic Mapping and Exploration}

@@

\institute{\footnotesize
{\\
\vspace*{0.3cm}
\normalsize Evan Kaufman}\\
\vspace*{0.3cm}
Robotic Research LLC
\\
\vspace*{0.3cm}
September 5, 2018
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Mobile Robotics
	\begin{itemize}
		\item Robots can replace humans dangerous/uncertain tasks such as surveillance, combat, and search-and-rescue
		\item Key question: when robots explore new spaces, how can they maximize their knowledge about their environment?
	\end{itemize}
	\pause
	\item Robotic Capabilities
	\begin{itemize}
		\item Robot must understand their environment by generating a map, referred to as \emph{mapping}
		\item Selecting and performing robotic actions to maximize map information, referred to as \emph{autonomous exploration}
		\item Cooperative robots can share information to achieve a collective goal with \emph{multi-vehicle exploration and patrol}
		\item These tasks must be performed in 2D and 3D environments, where computational efficiency is paramount to real-time implementation
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Research Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping
		\begin{itemize}
		\item Computation of the exact occupancy probability
		\item Incorporation of prior knowledge and new measurements
		\item Bayesian information fusion
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Novel approach to predicting future map uncertainty
		\item Optimal planning to maximize information gain
	\end{itemize}
	\pause
	\item Multi-Vehicle Exploration and Patrol
	\begin{itemize}
		\item Bidding-based framework for assigning tasks while exploring uncertain environments
		\item Map degradation to encourage revisiting regions from the past 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{enumerate}[I]
	\item Occupancy Grid Mapping
	\begin{itemize}
		\item Background and problem definition
		\item Common approaches and approximations
		\item Inverse sensor model in 1D
		\item Ray casting and measurement scans for 2D and 3D environments
		\item Numerical examples
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Existing solutions: frontiers, expected measurements
		\item Proposed approach: entropy expectation
		\item Collision-free trajectories
		\item Optimal pose selection
		\item Numerical examples
	\end{itemize}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Outline}
\begin{enumerate}[I]
\addtocounter{enumi}{2}
	\item Multi-Vehicle Exploration and Patrol
	\begin{itemize}
		\item Cooperative approaches
		\item Bidding-based framework
		\item Receding horizon
		\item Multi-vehicle autonomous exploration numerical example
		\item Autonomous patrol
		\item Multi-vehicle autonomous patrol numerical example
	\end{itemize}
	\pause
	\item Experiments
	\begin{itemize}
		\item Ground vehicle 2D mapping and autonomous exploration
		\item Aerial quadrotor in large vertically-uniform space
		\item Aerial quadrotor in complex 3D environment
	\end{itemize}
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Probabilistic Occupancy Grid Mapping}
\begin{enumerate}[I]
	\item Probabilistic Occupancy Grid Mapping
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Mapping Representation}
    \begin{itemize}
    	\item Simple and well-known grid-based representation
	\pause
	\item Decomposes space into evenly-spaced cells that are either \emph{occupied} or \emph{free}
	\pause
    	\item Probabilistic: goal is to find the \emph{probability} that the cells are occupied
	\pause
	\item Useful for collision-avoidance and graph searching
    \end{itemize}

@@

\begin{frame}
\frametitle{Approximate Solutions}

\begin{minipage}[t]{7.0cm}
\begin{itemize}
	\item Approximate a function for the inverse sensor model based on intuition
	\begin{itemize}
		\item Simple to implement, but mathematically inaccurate
	\end{itemize}
\end{itemize}
\end{minipage}
\begin{minipage}[t]{3.0cm}
\begin{figure}[!htbp]
\centerline{
    \vspace*{-0.5cm}
%	\hspace*{0.25cm}
    \includegraphics[width=4.0cm]{Approx_ISM_shortened.png}\hspace*{0.1cm}
    }
\centerline{
    \includegraphics[width=3.5cm]{1D_True_Grid.png}
%    \hspace*{0.75cm}
    }
		\end{figure}
\end{minipage}
\vspace*{-0.5cm}
\vspace*{0.0cm}\pause
\begin{itemize}
	\item Find a solution through learning
	\begin{itemize}
		\item Simulate maps, poses, and measurements and use learning to obtain an inverse sensor model
		\item Complicated, unclear how these parameters are chosen
	\end{itemize}
	\vspace*{0.0cm}\pause
	\item Goal: design a \emph{simple} and \emph{accurate} occupancy grid mapping method avoiding log-odds ratio assumptions
\end{itemize}

\begin{frame}
\frametitle{Proposed Approach: Utilize Invariance}

\begin{itemize}
    \item Main idea: make use of occupancy grid mapping \emph{assumptions} and extract \emph{patterns} from probabilistic properties to find a \emph{computationally-efficient} solution
	\begin{itemize}
		\item Since the origin and direction of each measurement ray is known deterministically, the set of grid cells that the ray intersects is \emph{known through geometry}
		\item A depth reading follows the forward sensor model, which \emph{only depends} on the first occupied grid cell along the measurement ray
	\end{itemize}
\end{itemize}
\setcounter{subfigure}{0}
% uncomment
\begin{figure}
  \centering
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_1.png}
  \end{subfigure}
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_2.png}
  \end{subfigure}
    \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_3.png}
  \end{subfigure}
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_4.png}
  \end{subfigure}
\end{figure}

@@

% Ray Casting

%\begin{frame}
%\frametitle{Ray Casting}
%
%\begin{itemize}
%	\item Required for 2D and 3D occupancy grid maps
%	\item Main idea: use simple geometry to find the distance from the robot sensor to each cell intersected by the measurement ray
%\end{itemize}
%
%\begin{figure}[!ht]
%    \centering
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth]{RayCastingIllustration.png}
%%        \label{fig:penn_map_total}
%    \end{subfigure}
%    \hspace*{0.05\columnwidth}
%    \begin{subfigure}[t]{0.4\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth]{RayCastIllustrationReducedMapOnly.png}
%%        \label{fig:penn_map_zoom}
%    \end{subfigure}
%\end{figure}
%
%\end{frame}

%\begin{frame}
%\frametitle{Scan Combination Approaches}
%
%\begin{itemize}
%	\item \emph{Ray-By-Ray Update}: given a scan of measurement rays, update the map based on each measurement ray \emph{individually} and \emph{sequentially}
%	\begin{itemize}
%		\item Benefit: the measurement rays maintain some dependency as they capture the same map
%		\item Drawback: the best order for evaluating rays is not necessarily chosen
%	\end{itemize}
%%	\item Conditional probability:
%%	\begin{align*}
%%		P(\mathbf{m}_i|X_{1:t}&,Z_{1:t})\nonumber\\&
%%		=P((\dots(((\mathbf{m}_i|X_{1:t},Z_{1:t-1})|z_{t,1})|z_{t,2})|\ldots)|z_{t,n_z})
%%	\end{align*}
%	\item \emph{Synergistic Update}: consider every measurement ray inside a scan \emph{simultaneously} to update all grid cells inside the FOV
%	\begin{itemize}
%		\item Benefit: synergistic update provides a method where all rays are considered simultaneously
%		\item Drawback: required assumption that the measurement rays are independent, though they capture the same map
%	\end{itemize}
%\end{itemize}
%
%\end{frame}

\begin{frame}
\frametitle{Numerical Example}

\begin{itemize}
	\item A standard \emph{approximate} inverse sensor model technique is compared with the proposed \emph{exact} method
	\item The exact algorithm yields a more \emph{certain} map from the same measurement set
\end{itemize}

%\vspace*{0.5cm}
\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_19.pdf}
        \caption*{Approx. Map}
    \end{subfigure}
%    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_19.pdf}
        \caption*{Exact Map}
    \end{subfigure}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{AISM_Image_inf_19.pdf}
        \caption*{Approx. $H$}
    \end{subfigure}
%    \hspace*{-0.1\textwidth}
    \begin{subfigure}{0.2\textwidth}
        \centering
        \includegraphics[width=\textwidth]{EISM_Image_inf_19.pdf}
        \caption*{Exact $H$}
    \end{subfigure}
\end{figure}

\begin{frame}
\frametitle{Probabilistic Occupancy Grid Mapping Summary}

\begin{itemize}
	\item The proposed novel Bayesian solution to the inverse sensor model provides the exact solution without approximate functions or learned solutions
	\item The computational complexity is linear with respect to the number of cells considered, making real-time implementation possible
	\item 2D and 3D maps are updated with ray casting and ray-by-ray combination
\end{itemize}

@@

\begin{frame}
\frametitle{Entropy-Based Autonomous Exploration}
\begin{enumerate}[I]
\addtocounter{enumi}{1}
	\item Entropy-Based Autonomous Exploration
\end{enumerate}
\end{frame}

@@

\begin{frame}
\frametitle{Expected Information Gain Computation}

\begin{itemize}
	\item \emph{Squared Complexity}: $\mathcal O(n_r^2)$ for $n_r$ cells along the ray
	\vspace*{0.0cm}\pause
	\item Two Approaches:
	\begin{itemize}
		\vspace*{0.0cm}\pause
		\item Decrease the cells considered by selecting $n_p$ most probable cells: $\mathcal O(n_r^2)$ reduces to $\mathcal O(n_p^2)$
		\vspace*{0.0cm}\pause
		\item Use 3D cells in a 2D \emph{projection}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.3\linewidth}
    \centering\includegraphics[height=.75\linewidth]{experiment_ogm3D_2min47sec.jpg}
    \caption*{\ \ \ \ \ \ \ \ \ \ \ \ \ \ 3D Map}
  \end{subfigure}
  \hspace*{0.25\linewidth}
  \begin{subfigure}[t]{.3\linewidth}
    \centering\includegraphics[height=.75\linewidth]{experiment_2min47sec.jpg}
    \caption*{2D Projection}
  \end{subfigure}
\end{figure}
	\end{itemize}
\end{itemize}

@@

@@

%\begin{frame}
%	\frametitle{2D Autonomous Exploration: Intel Research Lab}
%	\centering{
%		\includemedia[
%  		width=\textwidth,
%  		height=0.8\textwidth,
%  		activate=pageopen,
%  		addresource=IRL.mp4,
%  		flashvars={source=IRL.mp4}
%		]{}{VPlayer.swf}
%		}
%\end{frame}

\begin{frame}
	\frametitle{3D Autonomous Exploration: Mars}
	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Topological Mars Mapping and Autonomous Exploration in 3D.mp4,
  		flashvars={source=Topological Mars Mapping and Autonomous Exploration in 3D.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

\begin{frame}
\frametitle{Autonomous Exploration Summary}

\begin{itemize}
	\item Other approaches use heuristic frontiers or entropy of expected measurements
	\item The proposed approach solves for the expected value of future map entropy directly
	\item Several sample future measurement rays and Dijkstra's cost map combine in an objective function for optimality
	\item A numerical simulation shows that this approach can be extended to 3D environments
\end{itemize}

\section*{}
\subsection*{Multi-Vehicle Exploration and Patrol}

\begin{frame}
\frametitle{Multi-Vehicle Exploration and Patrol}
\begin{enumerate}[I]
\addtocounter{enumi}{2}
	\item Multi-Vehicle Exploration and Patrol
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Motivation and Goal}

\begin{itemize}
	\item Multi-Vehicle Autonomous Exploration
	\begin{itemize}
		\item Multiple agents can accomplish tasks faster and more reliably than a single agent
		\item Large groups are capable of coverage in large environments
		\item Problem: multi-vehicle map information gain optimality can be computationally-intractable
		\item Approach: bidding-based solution simplifies a complicated optimization into a series of simplified optimizations
	\end{itemize}
	\pause
	\item Multi-Vehicle Autonomous Patrol
	\begin{itemize}
		\item Patrolling large environments with humans is expensive and sometimes dangerous
		\item Several robotic approaches introduce new variables for patrol
		\item Approach: degrade probabilistic occupancy grid over time to encourage revisiting past regions
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Related Work in Multi-Vehicle Exploration}

\begin{itemize}
	\item Most existing bidding-based techniques deal with auctioning tasks among a few agents locally in decentralized frameworks
	\item The other approach is for a central executive to run a series of auctions
	\item Bids are discounted between auctions to coordinate the efforts based on coverage overlap
	\item Heuristic, ad hoc
\end{itemize}

\begin{frame}
\frametitle{Proposed Approach in Multi-Vehicle Exploration}

\begin{itemize}
\item Central executive completes $n$ auctions for $n$ robots
\begin{enumerate}
	\item Each robot determines its optimal future pose, and bids the objective function
	\item The winner is awarded this future pose, and the remaining robots update their bids according to
	\begin{itemize}
		\item New expected map changes from the winner
		\item Collision-avoidance with the winner
	\end{itemize}
	\item Repeat these steps with the remaining robots
\end{enumerate}
\item The efforts are coordinated by updating bids between auctions
\item The algorithm follows a receding-horizon framework: future pose optimization repeats as quickly as possible
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Numerical Example: SEH Multi-Vehicle Exploration}

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Mapping and Exploration.mp4,
  		flashvars={source=Multi-Vehicle Mapping and Exploration.mp4}
		]{}{VPlayer.swf}
		}

\begin{frame}
\frametitle{Cooperative Autonomous Patrol}

\begin{itemize}
	\item Existing Approaches
	\begin{itemize}
		\item Rely on a known map and use Voronoi diagrams to disperse
		\item Another approach introduces cell periodicity: observe long-term dynamics of objects at the same location on the occupancy grid
		\item Bio-inspired approach uses digital pheromones 
		\item Minimizing robot idleness
	\end{itemize}
	\pause
	\item Proposed Approach
	\begin{itemize}
		\item Degrade occupancy grid cells toward their initial values with exponential decay
		\item Only affects existing probability values without new variables to track
		\item Promotes exploration first, then patrol
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Continuous-Time Markov Process}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{markov_diagram_continuous.pdf}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.6\textwidth]{DegradeExamples.pdf}
\end{figure}

\begin{frame}
\frametitle{Numerical Example: SEH Multi-Vehicle Patrol}

	\centering{
		\includemedia[
    		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Multi-Vehicle Cooperative Patrol.mp4,
  		flashvars={source=Multi-Vehicle Cooperative Patrol.mp4}
		]{}{VPlayer.swf}
		}

\begin{frame}
\frametitle{Cell Degradation and Patrol}

\begin{figure}
	\centering
	\includegraphics[width=0.65\textwidth]{entropy_patrol_9minSwitch.pdf}
\end{figure}

\begin{itemize}
	\item Entropy of the map increases if patrol stops at $9$ minutes if cell degradation continues
\end{itemize}

\begin{frame}
\frametitle{Multi-Vehicle Exploration and Patrol Summary}

\begin{itemize}
	\item Robotic tasks are assigned following a bidding-based framework to avoid a computationally-intractable solution
	\item Only one robot wins an auction, and bids are updated for the remaining robots in subsequent auctions
	\item A receding-horizon framework optimizes the time to update the optimal future poses
	\item Cell degradation provides a simple means for autonomous patrol via a continuous-time Markov process
	\item Numerical examples of a large experimental space demonstrate both algorithms
\end{itemize}
\end{frame}

\section*{}
\subsection*{Experiments}

\begin{frame}
\frametitle{Experiments}
\begin{enumerate}[I]
\addtocounter{enumi}{3}
	\item Experiments
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Experimental Overview}

\begin{enumerate}
	\item Ground vehicle experiment for 2D occupancy grid mapping and autonomous exploration
	\item Aerial vehicle experiment in large 3D space resembling an office
	\item Aerial vehicle experiment in a complex 3D space
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Pioneer Ground Vehicle 2D Example}
\begin{itemize}
        	\item A pioneer ground vehicle explores a room composed of Styrofoam walls
	\item Experiments use ROS, a Microsoft Kinect depth sensor, and Vicon Tracker for pose information
\end{itemize}
\begin{figure}
	\centering
    	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{pioneer.png}
        		\caption*{Pioneer}
    	\end{subfigure}    	
	\hspace*{0.04\textwidth}
	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_1.jpg}
        		\caption*{Bottom-left view}
    	\end{subfigure}
	\hspace*{0.03\textwidth}
	\begin{subfigure}[b]{0.28\textwidth}
        		\includegraphics[width=\textwidth]{test_setup_2.jpg}
        		\caption*{Bottom-right view}
    	\end{subfigure}
\end{figure}

\begin{frame}
\frametitle{Ground Experiment Video}

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=NRL_ground_test.mp4,
  		flashvars={source=NRL_ground_test.mp4}
		]{}{VPlayer.swf}
		}

\begin{frame}
\frametitle{Ground Vehicle Experimental Results}

\begin{figure}
	\centering{
    	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_start.jpg}
        		\caption*{$t=0.0$min}
        		\label{fig:Experiment_ogm_t0}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_0p5min.jpg}
        		\caption*{$t=0.5$min}
        		\label{fig:Experiment_ogm_t0p5}
    	\end{subfigure}    
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1min.jpg}
        		\caption*{$t=1.0$min}
        		\label{fig:Experiment_ogm_t1}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_1p5min.jpg}
        		\caption*{$t=1.5$min}
        		\label{fig:Experiment_ogm_t1p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2min.jpg}
        		\caption*{$t=2.0$min}
        		\label{fig:Experiment_ogm_t2}
    	\end{subfigure}
		\vspace*{0.05\textwidth}

	}
	\vspace*{-1cm}
	\centering{
    	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_2p5min.jpg}
        		\caption*{$t=2.5$min}
        		\label{fig:Experiment_ogm_t2p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3min.jpg}
        		\caption*{$t=3.0$min}
        		\label{fig:Experiment_ogm_t3}
    	\end{subfigure}    
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_3p5min.jpg}
        		\caption*{$t=3.5$min}
        		\label{fig:Experiment_ogm_t3p5}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4min.jpg}
        		\caption*{$t=4.0$min}
        		\label{fig:Experiment_ogm_t4}
    	\end{subfigure}
	\begin{subfigure}[b]{0.19\textwidth}
        		\includegraphics[trim={13cm 1cm 13cm 0}, clip, width=\textwidth]{t_4p5min.jpg}
        		\caption*{$t=4.5$min}
        		\label{fig:Experiment_ogm_t4p5}
    	\end{subfigure}
	}
\end{figure}

\begin{frame}
\frametitle{Aerial Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Hardware
	\begin{itemize}
		\item NVIDIA Jetson Ubuntu computer-on-module
		\item Asus Xtion IR color depth sensor
		\item Hokuyo LIDAR
		\item VectorNav IMU
	\end{itemize}
	\item Software
	\begin{itemize}
		\item Robot Operating System (ROS)
		\item Vicon Tracker (mocap\_vicon)
		\item Geometric Control: coordinate-free attitude control
	\end{itemize}
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_top.png}
    \caption*{Quadrotor Top}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[height=.5\linewidth]{quad_bottom.png}
    \caption*{Quadrotor Bottom}
  \end{subfigure}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Aerial Vehicle in a Large Office-Like Environment}
\begin{itemize}
        	\item Environment Size: $10.8$ m $\times$ $11.8$ m $\times$ $1.65$ m
\end{itemize}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[width=\linewidth]{experiment_north.jpg}
    \caption*{North Region}
  \end{subfigure}
  \begin{subfigure}[t]{.4\linewidth}
    \centering\includegraphics[width=\linewidth]{experiment_south.jpg}
    \caption*{South Region}
  \end{subfigure}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Large Flight Test Experiment Video}

	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=NRL_3D_large_space.mp4,
  		flashvars={source=NRL_3D_large_space.mp4}
		]{}{VPlayer.swf}
		}

\begin{frame}
\frametitle{Aerial Vehicle in a Complex 3D Environment}
\begin{itemize}
        	\item Full 3D mapping and exploration
	\item Objects are not vertically-uniform
	\item Environment Size: $9.0$ m $\times$ $8.5$ m $\times$ $2.25$ m
\end{itemize}

@@

\begin{frame}
\frametitle{Experiment Summary}
\begin{itemize}
        	\item Experimental environments in 2D and 3D are modeled with occupancy grids
	\item Future entropy prediction and collision-free regions use these occupancy probabilities
	\item A geometric controller is used during flight testing to follow the collision-free trajectory
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Future Directions}
	\begin{itemize}
		\item Localization: use probabilistic map and other onboard sensors to localize, thereby completing the SLAM problem with the novel mapping approach
		\item Computational improvements: determine collision-free costs more efficiently than Dijkstra's cost map
		\item Decentralize the algorithms so processes may be distributed among multiple agents
	\end{itemize}
\end{frame}

>>>>

\setbeamertemplate{footline}%{split theme}
{%
  \leavevmode%
  \hbox{\begin{beamercolorbox}[wd=.85\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm plus1fill]{author in head/foot}%
    \usebeamerfont{author in head/foot}\insertshorttitle
  \end{beamercolorbox}%
  \begin{beamercolorbox}[wd=.15\paperwidth,ht=2.5ex,dp=1.125ex,leftskip=.3cm,rightskip=.3cm]{title in head/foot}
    \usebeamerfont{title in head/foot}\mypaper\hfill \insertframenumber/\inserttotalframenumber
  \end{beamercolorbox}}%
  \vskip0pt%
} \setbeamercolor{box}{fg=black,bg=yellow}

\title[Autonomous Aerial Exploration for Topological Mapping of Mars Environments]{\large Autonomous Aerial Exploration for Topological Mapping of Mars Environments}

@@

\institute{\footnotesize
{\\
\vspace*{0.3cm}
\normalsize Evan Kaufman and Taeyoung Lee}
\\
\vspace*{0.3cm}
January 10, 2019
}

@@

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
	\item Topography of Mars
	\begin{itemize}
		\item Future mission planning
		\item Spacecraft landing
		\item Image distortion correction
		\item The Mars Orbiting Laser Altimeter (MOLA) uncertainty is about $8$ meters
	\end{itemize}
	\pause
	\item Mars Rovers for Mapping Mars
	\begin{itemize}
		\item Four successful driving missions, Curiosity still functional and communicating
		\item Driving robots are incapable of traversing steep or dangerous terrain
		\item Humans cannot control rovers directly due to a time delay from Earth
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Research Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping
		\begin{itemize}
		\item Computation of the exact occupancy probability of the initially-uncertain Mars environment
		\item Incorporation of prior knowledge and new measurements
		\item Bayesian information fusion in 3D
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Novel approach to predicting future map uncertainty
		\item Optimal planning to maximize information gain
		\item Complicated 3D Mars environment explicitly considered in pose selection and path planning
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}
\frametitle{Mapping Representation}
    \begin{itemize}
    	\item Simple and well-known grid-based representation
	\pause
	\item Decomposes space into evenly-spaced cells that are either \emph{occupied} or \emph{free}
	\pause
    	\item Probabilistic: goal is to find the \emph{probability} that the cells are occupied
	\pause
	\item Useful for collision-avoidance and path-planning
    \end{itemize}

@@

\begin{frame}
\frametitle{Inverse Sensor Model with Invariance}

\begin{itemize}
    \item Main idea: make use of occupancy grid mapping \emph{assumptions} and extract \emph{patterns} from probabilistic properties to find a \emph{computationally-efficient} solution
	\begin{itemize}
		\item Since the origin and direction of each measurement ray is known deterministically, the set of grid cells that the ray intersects is \emph{known through geometry}
		\item A depth reading follows the forward sensor model, which \emph{only depends} on the first occupied grid cell along the measurement ray
	\end{itemize}
\setcounter{subfigure}{0}
% uncomment
\vspace*{-0.03\textwidth}
\begin{figure}
  \centering
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_1.png}
  \end{subfigure}
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_2.png}
  \end{subfigure}
    \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_3.png}
  \end{subfigure}
  \begin{subfigure}[t]{.45\linewidth}
    \centering\includegraphics[width=\linewidth]{rkplus_4.png}
  \end{subfigure}
\end{figure}
	\item Avoids common approximated or learned solutions
\end{itemize}

@@

@@

@@

\begin{frame}
\frametitle{Pose Information Gain in 2D}

@@

\begin{frame}
\frametitle{Pose Information Gain in 3D}

\begin{itemize}
	\item Several sample pitch angles per horizontal direction
	\item Optimal attitude assuming level flight, i.e., zero roll/pitch
	\item Consideration of grid cells above and below the vehicle
\end{itemize}
\begin{figure}[!t]
	\centering
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {21cm 5cm 20cm 5cm}, clip, height=1.0\textwidth]{mars_general.png}
        		\caption{General View}
    	\end{subfigure}
    	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {25cm 6cm 16cm 4cm}, clip, height=1.0\textwidth]{mars_psi.png}
        		\caption{$\psi$ Rotation}
    	\end{subfigure}
	\begin{subfigure}[t]{0.3\columnwidth}
           	\centering
          	\includegraphics[trim = {23cm 4cm 17cm 6cm}, clip, height=1.0\textwidth]{mars_theta.png}
        		\caption{$\theta$ Rotation}
    	\end{subfigure}
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
\label{fig:transforms}
\end{figure}
\end{frame}

@@

\begin{frame}
\frametitle{Optimal Pose Selection in 3D}

\begin{itemize}
	\item Apply Dijkstra's algorithm about 3D graph of occupancy grid
	\item Locations and associated distance costs for reachable positions in 3D
\end{itemize}
\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{mars_closeup.png}
        		\caption{Mars Simulation Poses}
    	\end{subfigure}
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{disconnected_costmap.png}
        		\caption{3D Dijkstra's Search}
    	\end{subfigure}
\label{fig:marsZoomedIn}
\end{figure}
\end{frame}

\begin{frame}
	\frametitle{3D Mars Exploration Conclusions}
	\begin{itemize}
		\item Expected information gain of several poses in 3D space capturing complex obstacles
		\item Distance cost accounts for collision-avoidance
		\item Mapping and exploration are computationally-efficient for real-time implementation
	\end{itemize}
		\begin{figure}
		\centerline{
			\includegraphics[width=0.8\columnwidth]{node_diagram_3D_mars.png}
		}
		\label{fig:NodesDiagram}
	\end{figure}
\end{frame}

\section*{}
\subsection*{Numerical Simulation \& Experiment}

\begin{frame}
	\frametitle{3D Autonomous Exploration Mars}
	\begin{itemize}
		\item A color image of Mars is draped over its height map using the Gazebo simulator
		\item Mapping and autonomous exploration are run in real-time using ROS nodes
		\item 3D depth measurements are simulated with Gaussian noise
		\item The robot is free to move within free space inside a fixed 3D volume
	\end{itemize}
	\begin{figure}[!t]
		\centering
		\begin{subfigure}[t]{0.3\columnwidth}
           		\centering
          		\includegraphics[height=0.9\textwidth]{mars_heightmap.png}
        			\caption{Height Map}
    		\end{subfigure}
    		\begin{subfigure}[t]{0.3\columnwidth}
			\centering
			\includegraphics[height=0.9\textwidth]{mars_colormap.png}
      	  		\caption{Color Map}
   	 	\end{subfigure}
  	  	\begin{subfigure}[t]{0.3\columnwidth}
			\centering{
          		\includegraphics[height=0.9\textwidth]{mars_gazebo_full_lighting.png}}
        			\caption{Gazebo}
    		\end{subfigure}
	\label{fig:MarsGazebo}
	\end{figure}
\end{frame}

\begin{frame}
	\frametitle{Mars Video}
	\centering{
		\includemedia[
  		width=\textwidth,
  		height=0.8\textwidth,
  		activate=pageopen,
  		addresource=Topological Mars Mapping and Autonomous Exploration in 3D.mp4,
  		flashvars={source=Topological Mars Mapping and Autonomous Exploration in 3D.mp4}
		]{}{VPlayer.swf}
		}
\end{frame}

\begin{frame}
\frametitle{Experiment: Aerial Vehicle in a Complex 3D Environment}
\begin{itemize}
        	\item Full 3D mapping and exploration
	\item Objects are not vertically-uniform
	\item Environment Size: $9.0$ m $\times$ $8.5$ m $\times$ $2.25$ m
\end{itemize}

@@

\begin{frame}
\frametitle{Experiment Summary}
\begin{itemize}
        	\item Environments in complex 3D are modeled with occupancy grids in simulation and experimentation
	\item Predicted entropy of certain and uncertain spaces provide a policy for 3D autonomous exploration
	\item Dijkstra's search provides a collision-free path and estimated travel costs that account for obstacles
	\item All algorithms are run in real-time without expensive post-processing 
\end{itemize}
\end{frame}

@@
